Biodiversity improves tropical forest resilience

### 2018-12-13 S1-LL.Rmd
Draft 0.1.9010 Co-authors sharing

---
title: "Supplementary material S1: Leaf lifespan model"
date: '`r Sys.Date()`'
output:
  bookdown::word_document2: default
  bookdown::html_document2:
    number_sections: no
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: no
    toc: no
    keep_tex: yes
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

>>>>

---
title: 'Supplementary material S1: Leaf lifespan model'
date: '`r Sys.Date()`'
output:
  bookdown::word_document2: default
  bookdown::html_document2:
    number_sections: no
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: no
    toc: no
    keep_tex: yes
  gdoc::gdoc: default
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
gdoc_id: 1G5GQy7yxmwSsUCcC_Exky_cPYDhwHxNcVXnnILdPAUs
---

### 2018-12-13 draft.Rmd
Draft 0.1.9010 Co-authors sharing

---
title: Biodiversity improves tropical forest resilience
author: Sylvain Schmitt, Isabelle Maréchaux, Jerome Chave, Fabian Fischer, Camille
  Piponiot, Stéphane Traissac & Bruno Hérault
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: no
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: no
    toc: no
    keep_tex: yes
  gdoc::gdoc: default
  bookdown::word_document2: default
linestretch: 1.5
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
gdoc_id: 1yRJitcL7DfCwTmZlUEuQEJg4-QcTfsznYqJ999VV-p8
---

>>>>

---
title: Biodiversity improves tropical forest resilience
author: Sylvain Schmitt, Isabelle Maréchaux, Jerome Chave, Fabian Fischer, Camille
  Piponiot, Stéphane Traissac & Bruno Hérault
date: '`r Sys.Date()`'
output:
  bookdown::word_document2: default
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: no
    toc: no
    keep_tex: yes
  gdoc::gdoc: default
  bookdown::html_document2:
    number_sections: no
    toc: yes
    toc_float: yes
linestretch: 1.5
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
gdoc_id: 1yRJitcL7DfCwTmZlUEuQEJg4-QcTfsznYqJ999VV-p8
---
